---
title: "Publications"
toc: true
bibliography: publications.bib
csl: apa.csl
format:
  html:
    css: pub-style.css
    include-in-header:
      - text: |
          <script src="publications.js"></script>
nocite: |
  @*
execute:
  echo: false
  warning: false
  message: false
  freeze: auto
---
<!-- code modified from https://github.com/jmgirard/affcomlab/tree/main --> 

This page lists all papers published by **Dr. Kevin Bladon and the FEWS Lab**, organized by year of publication. 

- Click a paper’s *title* to visit the publisher page and access the official version. 
- Use *Abstract* to reveal the summary, *Citation* for the APA 7th-edition reference, and *BibTeX* to view the BibTeX entry. 
- *Article* links to a free version of the publication. 
- *Preprint* links to a pre-print that has not been peer-reviewed.
- *Materials* leads to a data package or open repository with data, code, and other open-science resources. 

<span style="font-size:0.9rem; opacity:0.8; margin-bottom:0.5rem;">★ = Work led or co-led by our lab</span>


```{r setup}
#loads packages and functions needed
source("publication-utils.R")
```

```{r}
#| label: create-bib 

#get id for group 
  user <- Sys.getenv("ZOTERO_USER_ID")
  collection <- "FEWS-publications"
  
  bib_id <- collection_ids(user, collection)
  
  #check for what types to include
  check <- zbib(bib_id, format = "json")
  types <- unique(sapply(check, function(x){x$data$itemType})) 
  types <- types[!types %in% c("attachment", "note")]
  
bib_list <- zbib(bib_id, format = "json", itemType = paste(types, collapse=" || "))
bib <- zbib(bib_id, format = "bibtex", itemType = paste(types, collapse=" || "))

#make sure that keys are unique 
  keys <- sapply(bib_list, function(x){x$data$citationKey})
  stopifnot(length(keys) == length(unique(keys)))
  
#apply extra info (pull just the things we want)
  bib_extra <- lapply(bib_list, pull_fields)

#copy pdf to website repo folder 
 move_pdfs(bib_list)
  
#save as yaml to read via quarto code
  yaml::write_yaml(bib_extra, "publications.yml")
  
#write bibtext file
  write.table(bib, "publications.bib", row.names=FALSE, col.names = FALSE, quote = FALSE)

```


```{r}
#| label: build-rows

#for debugging
  #bib_extra  <- yaml::read_yaml("publications/publications.yml")
  #bib  <- ReadBib("publications/publications.bib", check = TRUE)

bib_extra  <- yaml::read_yaml("publications.yml")
bib  <- ReadBib("publications.bib", check = TRUE)
rows <- create_rows(bib, bib_extra)

```

## Peer-Reviewed Publications

```{r}
#| label: render-publications-submit

years <- "In Review"

groups <- lapply(years, function(y) {
  subset <- rows |> filter(inreview & !informal)
  subset_min <- subset |>
    select(
      key, entry, has_preprint_key, has_materials_key, title, 
      authors_card, year, venue,
      abstract, bibtex, 
      preprint_url, materials_url, 
      article_url, doi_url, primary,
      inreview
    )
  cards <- pmap(subset_min, build_card)

  tags$div(
    class = "year-group",
    tags$h2(class = "year-title anchored", id = paste0("y-", y), str_to_title(y)),
    tags$div(cards)
  )
})

browsable(tags$div(
  groups
))
```


```{r}
#| label: render-publications-peer

years <- rows |> filter(!inreview & !informal) |>
  distinct(year) |>
  arrange(desc(year)) |>
  pull(year)

groups <- lapply(years, function(y) {
  subset <- rows |> filter(year == y & !inreview & !informal)
  subset_min <- subset |>
    select(
      key, entry, has_preprint_key, has_materials_key, title, 
      authors_card, year, venue,
      abstract, bibtex, 
      preprint_url, materials_url, 
      article_url, doi_url, primary,
      inreview
    )
  cards <- pmap(subset_min, build_card)

  tags$div(
    class = "year-group",
    tags$h2(class = "year-title anchored", id = paste0("y-", y), str_to_title(y)),
    tags$div(cards)
  )
})

browsable(tags$div(
  groups
))
``` 

## Refereed Technical and Extension Publications

```{r}
#| label: render-publications-informal

years <- rows |> filter(!inreview & informal) |>
  distinct(year) |>
  arrange(desc(year)) |>
  pull(year)

groups <- lapply(years, function(y) {
  subset <- rows |> filter(year == y & informal)
  subset_min <- subset |>
    select(
      key, entry, has_preprint_key, has_materials_key, title, 
      authors_card, year, venue,
      abstract, bibtex, 
      preprint_url, materials_url, 
      article_url, doi_url, primary,
      inreview
    )
  cards <- pmap(subset_min, build_card)

  tags$div(
    class = "year-group",
    tags$h2(class = "year-title anchored", id = paste0("y-", y), str_to_title(y)),
    tags$div(cards)
  )
})

browsable(tags$div(
  groups,
  tags$hr(),
  tags$div(
    class = "code-attribution",
    "Publication card functionality adapted from ",
    tags$a(
      "AffCom Lab",
      href = "https://affcom.ku.edu/publications.html",
      target = "_blank",
      rel = "noopener"
    ),
    "."
  )
))
```